Functions Created

### 2017-07-22 freq_words.Rmd
reorganized files and code, made code more reproducible, updated hours, deleted files

---
title: "New variables"
author: "Lisa Oshita"
date: "July 14, 2017"
output: html_document
---

@@

### importing the data/setting up variables
```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

out$time_until_answer <- out$first_answer_date - out$post_date
#filling in the NAs
empty <- which(is.na(out$time_until_answer))
for (i in empty) {
  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
}

library(dplyr)
out_english <- out %>% 
                tbl_df() %>% 
                filter(langid == "en")
```

### finding most frequently used terms
```{r}
library(qdap)
library(tm)
#library(RWeka)

#function to clean the corpus
clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
  return(corpus)
}

freq_terms <- function(vec) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus)
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  return(freq)
}

titles_freq <- freq_terms(out_english$title)
head(titles_freq)
#this function changes "turn on" to just "turn", in our case "turn on" might be a significant term? -- do something about this in the function? like do bigrams? (observation 300)

top100 <- titles_freq[1:100]
top50 <- titles_freq[1:50]
top10 <- titles_freq[1:10]
plot(term_freq)
plot(top50)
```

### variable indicating if title contains at least one word in top50 words list
```{r}
library(stringr)
library(rebus)

out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
```

### exploring contain_top10
```{r}
sum(out_english$contain_top10)/nrow(out_english)
#41% of words contain at least one of the top 10 words

library(dplyr)
#not working correctly???
out_english %>%
  group_by(contain_top10) %>%
  summarise(median_time = median(time_until_answer), 
            avg_daily = mean(daily_views)) %>%
  arrange(median_time)

hist(unname(titles_freq))
hist(log(titles_freq))
hist(log(out_english$time_until_answer))

t.test(log(time_until_answer) ~ contain_top10, data = out_english)
```

### survival curves
```{r}
library(survival)

surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")

options(scipen=5)
KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
plot(KM_top10, lty = 1:2, xlab = "Time", ylab = "Survival Probability", main = "KM Curves for questions with and without top 10 terms")
legend("topright", c("False", "True"), lty = 1:2)

survdiff(surv_object~contain_top10, data = out_english)
```

### trying out TfIdf (counts occurrences of words but penalizes for appearing in too many documents) 
```{r}
freq_terms_weighted <- function(vec) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = function(x)
    weightTfIdf(x, normalize = TRUE)))
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  return(freq)
}

titles_freq_weighted <- freq_terms_weighted(out_english$title)
top10_weighted <- term_freq_weighted[1:10]
top10_weighted
top50_weighted <- term_freq_weighted[1:50]

hist(titles_freq_weighted)

#weighting didn't do much
```

### visualizing the frequency of the words

also look at the distribution of how often the appear (plot of 100 words verses percent of posts appeared in) 
top 20 words—might be in 80% of the words
add up words cumulatively? use a cumulative function in r, make own table manually (word number vs percent post appears in , then use cumulative function on that table to create plot) 
```{r}

plot(x = c(1:50), unname(top50)/nrow(out_english), xlab = "Top 10 terms", ylab = "Percentage of posts appeared in", xaxt = "n")
axis(1, at=1:50, labels=names(top50), las = 2)
#screen appears in 12% of questions

#cumulative distribution
cum_percent <- cumsum(unname(top10))
plot(x = c(1:10), cum_percent/nrow(out_english), xlab = "Top 10 Terms", ylab = "Cumulative Percentage of posts appeared in", xaxt = "n")
axis(1, at=1:10, labels=names(top10), las = 2)
# this is "double counting" questions? 
```

* find most frequent terms among answered/unanswered questions
* if any of these terms are present in a question, can use to predict the time_until_answer (think that questions that contain terms in frequent terms list in answered questions might get answered quicker, questions that contain terms in list for unanswered questions might get answered slower)
* noticed that there were shared common words among answered/unanswered questions (ex: screen, phone)
* wanted to find a way to find words unique to answered/unanswered 
* calculating proportion of times that each word in the most freq list occurs in its answered or unanswered category 
* finding the difference in these proportions to see if the word is more likely to be in answered/unanswered category 
*use these difference in proportions to determine which list the term should be included in (answered/unanswered)

```{r}
library(tidyverse) #contains all packages
library(plyr)
answered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 1)
unanswered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 0)

answered_m <- freq_terms(answered$title)
unanswered_m <- freq_terms(unanswered$title)

answered_m[1:100]
unanswered_m[1:100]

str(answered_m)

#proportion of times each term occurs in answered/unanswered questions
answered_freq <- data.frame(term = names(answered_m), a_freq = unname(answered_m), a_prop = unname(answered_m)/length(answered_m))

unanswered_freq <- data.frame(term = names(unanswered_m), u_freq = unname(unanswered_m), u_prop = unname(unanswered_m)/length(unanswered_m))

combined <- join(answered_freq, unanswered_freq, by = "term", match = "all")
head(combined)
dim(combined)
```

```{r}
combined$difference <- abs(combined$a_prop - combined$u_prop)
combined$ratio <- combined$a_prop/combined$u_prop
head(combined)

combined %>%
  arrange(desc(ratio)) %>%
  select(-difference)
# ssd is 28.8 times more likely to appear in answered questions than it is in unanswered questions, only because it appears 40 times in a_freq questions and only once in unanswered 
# need to come up with min and max thresholds for which terms to include freq_words list

combined %>%
  arrange(desc(u_prop))

library(ggthemes)
ggplot(combined, aes(x = u_prop)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,500))

ggplot(combined, aes(x = a_prop)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,200)) 
```
* how many words to consider
* minimum/max occurence thresholds (how often show up to be able to use it) 
* create a function that takes in as parameter how many words to consider, and then 
*function to take in vector of text, return frequencies of top words, input = number of words to return 
*ggplot!!!!

>>>>

---
title: "Frequent Words"
output: html_document
---

@@

* **Idea: there are words that show up frequently among answered questions and unanswered questions, which might be able to be used as predictors in the model**

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
out_english <- out %>% 
                tbl_df() %>%
                filter(langid == "en")

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

library(stringr)
library(rebus)
library(survival) 
library(survminer)
library(tidyverse)
```

```{r, include = FALSE}
library(qdap)
library(tm)

#function to clean corpus
clean_corpus <- function(corpus){
  library(tm)
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
  return(corpus)
}

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n is an optional argument 
freq_terms <- function(vec, n = NULL) {
  library(qdap)
  library(tm)
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus)
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  freq_df <- data.frame(word = names(freq), frequency = unname(freq))

  if (is.null(n)) {
    return(freq_df)
  }
  else if (!is.null(n)) {
    return(freq_df[1:n,])
  }
}

#function to plot survival curves with ggplot
plot_surv <- function(survfit, data, ...) {
  library(ggfortify)
  library(directlabels)

  df <- fortify(survfit, data = data)

  if (!("strata" %in% names(df))) {
    ggplot(df, aes(x = time, y = surv)) + 
    geom_line() + 
    scale_y_continuous("Survival Probability") +
    scale_x_continuous("Time")
    ggtitle("Survival Curve")
  }

  if ("strata" %in% names(df)) {
    ggplot(df, aes(x = time, y = surv, color = strata)) + 
      geom_line() + 
      scale_y_continuous("Survival Probabilities") +
      scale_x_continuous("Time") + 
      ggtitle("Survival Curves") + 
      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
  }
}
```

### finding top10 and top50 most frequently used terms in titles

```{r, echo = FALSE}
titles_freq <- freq_terms(out_english$title)

ggplot(titles_freq, aes(x = frequency)) + 
  geom_histogram() + 
  ggtitle("Distribution of word frequencies")
```

```{r, echo = FALSE}
top50 <- titles_freq[1:50,]
top50$word <- factor(top50$word, levels = top50$word)

ggplot(top50, aes(x = word, y = frequency/nrow(out_english))) + 
  geom_point() +
  scale_y_continuous("Percentage of times the word appears", labels = scales::percent) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("How often the 50 most frequently used words appear")
```

##### top10 most frequently used words

```{r, echo = FALSE}
top10 <- titles_freq[1:10,]
out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
prop_contain <- sum(out_english$contain_top10)/nrow(out_english)
```

* `r round(prop_contain * 100, 2)`% of questions contain at least 1 of the top 10 most frequent words in the title

```{r, echo = FALSE}
top10
```

##### median time and average daily views grouped by whether or not question contains top10

```{r, echo = FALSE}
out_english %>%
  group_by(contain_top10) %>%
  summarise(median_time = median(time_until_answer), 
            avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

* table indicates that questions with titles that don't contain the top10 words may get answered faster

##### log-rank test

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
survdiff(surv_object~contain_top10, data = out_english)
```

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
plot_surv(KM_top10, data = out_english)
```

### Most frequent words within answered and unanswered questions

```{r, echo = FALSE}
answered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 1)
unanswered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 0)

terms_a <- freq_terms(answered$title)
terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
colnames(terms_a)[2] <- "frequency_a"

terms_u <- freq_terms(unanswered$title)
terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
colnames(terms_u)[2] <- "frequency_u"

combined <- full_join(terms_a, terms_u, by = "word")
combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
head(combined)
```

* data frame with frequency and proportion of times each word appears in both answered and unanswered questions, along with the ratio of proportion of times a word appears in answered questions to the proportion of times it appears in unanswered questions (ratio = prop_in_answered/prop_in_unanswered)

##### viewing proportions/frequencies arranged by ratio in decreasing order

* interpretation: "ssd" is 28.8 times more likely to show up in answered questions than it is in unanswered questions. But since it only shows up 0.7% of the time in answered questions, and 0.02% of the time in unanswered questions, this term might not be helpful in telling us whether or not a question is likely to be answered.

```{r, echo = FALSE}
head(combined %>% 
  arrange(desc(ratio)))
```

##### viewing proportions/frequencies arranged by proportion in unanswered questions, decreasing order 
```{r, echo = FALSE}
head(combined %>%
  arrange(desc(prop_in_unanswered)))
```

```{r, echo = FALSE}
ggplot(combined, aes(x = prop_in_answered)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous("Proportion in answered questions",limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,200)) + 
  ggtitle("Distribution of proportions in answered questions")
```

```{r, echo = FALSE}
ggplot(combined, aes(x = prop_in_unanswered)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous("Proportion in unanswered questions", limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,200)) + 
  ggtitle("Distribution of proportions in unanswered questions")
```

##### finding proportion and ratio thresholds

* find a set of words that show up frequently enough to be used as a set of predictors
* want the ratio to be large (or small) enough to allow us to decide whether or not that word is more likely to show up in an answered/unanswered question

###### words that appear more than 1% of the time in unanswered questions and are more likely (ratio < 1) to be used in unanswered questions
```{r, echo = FALSE}
p_threshold <- 0.01
ratio_threshold <- 1

freq_terms_u <- combined %>%
                  filter(prop_in_unanswered > p_threshold) %>%
                  filter(ratio < ratio_threshold)
freq_terms_u
```

###### words that appear more than 1% of the time in answered questions and are more likely (ratio > 1) to be used in answered questions

```{r, echo = FALSE}
freq_terms_a <- combined %>%
                  filter(prop_in_answered > p_threshold) %>%
                  filter(ratio > ratio_threshold)
freq_terms_a
```

### Summary statistics/survival analysis for whether or not questions contain frequent unanswered terms

```{r, echo = FALSE}
out_english$contain_u <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_u$word))

prop_contain_u <- sum(out_english$contain_u)/nrow(out_english)
```

* `r round(prop_contain_u * 100, 2)`% of questions contain at least one of the most frequent unanswered terms

##### median answer time and average daily views grouped by whether or not question contains at least 1 uanswered term

```{r, echo = FALSE}
out_english %>%
  group_by(contain_u) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u, data = out_english)
```

```{r, echo = FALSE}
KM_u <- survfit(surv_object ~ contain_u, data = out_english) 
plot_surv(KM_u, data = out_english)
```

### Summary statistics/survival analysis for whether or not questions contain frequent answered terms

```{r, echo = FALSE}
out_english$contain_a <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_a$word))

prop_contain_a <- sum(out_english$contain_a)/nrow(out_english)
```

* `r round(prop_contain_a * 100, 2)`% of questions contain at least one of the most frequent answered terms

##### median answer time and average daily views grouped by whether or not question contains at least 1 answered term

```{r, echo = FALSE}
out_english %>%
  group_by(contain_a) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object~contain_a, data = out_english)
```

```{r, echo = FALSE}
KM_a <- survfit(surv_object ~ contain_a, data = out_english)
plot_surv(KM_a, data = out_english)
```

#### looking at only device terms within freq_terms_u (discarding irrelevant words)
```{r, echo = FALSE}
unanswered_devices <- freq_terms_u %>%
                        filter(word %in% c("camera", "sound", "tablet", "light", "wifi", "speaker", "sound"))

out_english$contain_u_dev <- str_detect(as.character(out_english$title), pattern = or1(unanswered_devices$word))

prop_contain_u_dev <- sum(out_english$contain_u_dev)/nrow(out_english)
```

* `r round(prop_contain_u_dev*100, 2)`% of titles contain at least 1 unanswered device terms

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u_dev, data = out_english)

KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = out_english)
plot_surv(KM_u_dev, data = out_english)
```

#### Looking at only device terms within freq_terms_a

```{r, echo = FALSE}
answered_devices <- freq_terms_a %>%
                      filter(word %in% c("screen", "iphone", "phone", "battery", "button", "display", "macbook", "lcd", "board", "keyboard", "laptop", "home", "pro", "drive"))

out_english$contain_dev_a <- str_detect(as.character(out_english$title), pattern = or1(answered_devices$word))
prop_contain_a_dev <- sum(out_english$contain_dev_a)/nrow(out_english)
```

* `r round(prop_contain_a_dev*100, 2)`% of titles contain at least 1 answered device term

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_dev_a, data = out_english)

KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = out_english)
plot_surv(KM_dev_a, data = out_english)
```

### 2017-07-22 functions.Rmd
reorganized files and code, made code more reproducible, updated hours, deleted files

---
title: "Frequent Words"
output: html_document
---

@@

* **Idea: there are words that show up frequently among answered questions and unanswered questions, which might be able to be used as predictors in the model**

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

@@

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

library(stringr)
library(rebus)
library(survival) 
library(survminer)
library(tidyverse)
```

```{r, include = FALSE}
library(qdap)
library(tm)

#function to clean corpus
clean_corpus <- function(corpus){
  library(tm)
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
  return(corpus)
}

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n is an optional argument 
freq_terms <- function(vec, n = NULL) {
  library(qdap)
  library(tm)
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus)
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  freq_df <- data.frame(word = names(freq), frequency = unname(freq))

  if (is.null(n)) {
    return(freq_df)
  }
  else if (!is.null(n)) {
    return(freq_df[1:n,])
  }
}

#function to plot survival curves with ggplot
plot_surv <- function(survfit, data, ...) {
  library(ggfortify)
  library(directlabels)

@@

### finding top10 and top50 most frequently used terms in titles

```{r, echo = FALSE}
titles_freq <- freq_terms(out_english$title)

ggplot(titles_freq, aes(x = frequency)) + 
  geom_histogram() + 
  ggtitle("Distribution of word frequencies")
```

```{r, echo = FALSE}
top50 <- titles_freq[1:50,]
top50$word <- factor(top50$word, levels = top50$word)

ggplot(top50, aes(x = word, y = frequency/nrow(out_english))) + 
  geom_point() +
  scale_y_continuous("Percentage of times the word appears", labels = scales::percent) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("How often the 50 most frequently used words appear")
```

##### top10 most frequently used words

```{r, echo = FALSE}
top10 <- titles_freq[1:10,]
out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
prop_contain <- sum(out_english$contain_top10)/nrow(out_english)
```

* `r round(prop_contain * 100, 2)`% of questions contain at least 1 of the top 10 most frequent words in the title

```{r, echo = FALSE}
top10
```

##### median time and average daily views grouped by whether or not question contains top10

```{r, echo = FALSE}
out_english %>%
  group_by(contain_top10) %>%
  summarise(median_time = median(time_until_answer), 
            avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

* table indicates that questions with titles that don't contain the top10 words may get answered faster

##### log-rank test

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
survdiff(surv_object~contain_top10, data = out_english)
```

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
plot_surv(KM_top10, data = out_english)
```

### Most frequent words within answered and unanswered questions

```{r, echo = FALSE}
answered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 1)
unanswered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 0)

terms_a <- freq_terms(answered$title)
terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
colnames(terms_a)[2] <- "frequency_a"

terms_u <- freq_terms(unanswered$title)
terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
colnames(terms_u)[2] <- "frequency_u"

combined <- full_join(terms_a, terms_u, by = "word")
combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
head(combined)
```

* data frame with frequency and proportion of times each word appears in both answered and unanswered questions, along with the ratio of proportion of times a word appears in answered questions to the proportion of times it appears in unanswered questions (ratio = prop_in_answered/prop_in_unanswered)

##### viewing proportions/frequencies arranged by ratio in decreasing order

* interpretation: "ssd" is 28.8 times more likely to show up in answered questions than it is in unanswered questions. But since it only shows up 0.7% of the time in answered questions, and 0.02% of the time in unanswered questions, this term might not be helpful in telling us whether or not a question is likely to be answered.

```{r, echo = FALSE}
head(combined %>% 
  arrange(desc(ratio)))
```

##### viewing proportions/frequencies arranged by proportion in unanswered questions, decreasing order 
```{r, echo = FALSE}
head(combined %>%
  arrange(desc(prop_in_unanswered)))
```

```{r, echo = FALSE}
ggplot(combined, aes(x = prop_in_answered)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous("Proportion in answered questions",limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,200)) + 
  ggtitle("Distribution of proportions in answered questions")
```

```{r, echo = FALSE}
ggplot(combined, aes(x = prop_in_unanswered)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous("Proportion in unanswered questions", limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,200)) + 
  ggtitle("Distribution of proportions in unanswered questions")
```

##### finding proportion and ratio thresholds

* find a set of words that show up frequently enough to be used as a set of predictors
* want the ratio to be large (or small) enough to allow us to decide whether or not that word is more likely to show up in an answered/unanswered question

###### words that appear more than 1% of the time in unanswered questions and are more likely (ratio < 1) to be used in unanswered questions
```{r, echo = FALSE}
p_threshold <- 0.01
ratio_threshold <- 1

freq_terms_u <- combined %>%
                  filter(prop_in_unanswered > p_threshold) %>%
                  filter(ratio < ratio_threshold)
freq_terms_u
```

###### words that appear more than 1% of the time in answered questions and are more likely (ratio > 1) to be used in answered questions

```{r, echo = FALSE}
freq_terms_a <- combined %>%
                  filter(prop_in_answered > p_threshold) %>%
                  filter(ratio > ratio_threshold)
freq_terms_a
```

### Summary statistics/survival analysis for whether or not questions contain frequent unanswered terms

```{r, echo = FALSE}
out_english$contain_u <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_u$word))

prop_contain_u <- sum(out_english$contain_u)/nrow(out_english)
```

* `r round(prop_contain_u * 100, 2)`% of questions contain at least one of the most frequent unanswered terms

##### median answer time and average daily views grouped by whether or not question contains at least 1 uanswered term

```{r, echo = FALSE}
out_english %>%
  group_by(contain_u) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u, data = out_english)
```

```{r, echo = FALSE}
KM_u <- survfit(surv_object ~ contain_u, data = out_english) 
plot_surv(KM_u, data = out_english)
```

### Summary statistics/survival analysis for whether or not questions contain frequent answered terms

```{r, echo = FALSE}
out_english$contain_a <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_a$word))

prop_contain_a <- sum(out_english$contain_a)/nrow(out_english)
```

* `r round(prop_contain_a * 100, 2)`% of questions contain at least one of the most frequent answered terms

##### median answer time and average daily views grouped by whether or not question contains at least 1 answered term

```{r, echo = FALSE}
out_english %>%
  group_by(contain_a) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object~contain_a, data = out_english)
```

```{r, echo = FALSE}
KM_a <- survfit(surv_object ~ contain_a, data = out_english)
plot_surv(KM_a, data = out_english)
```

#### looking at only device terms within freq_terms_u (discarding irrelevant words)
```{r, echo = FALSE}
unanswered_devices <- freq_terms_u %>%
                        filter(word %in% c("camera", "sound", "tablet", "light", "wifi", "speaker", "sound"))

out_english$contain_u_dev <- str_detect(as.character(out_english$title), pattern = or1(unanswered_devices$word))

prop_contain_u_dev <- sum(out_english$contain_u_dev)/nrow(out_english)
```

* `r round(prop_contain_u_dev*100, 2)`% of titles contain at least 1 unanswered device terms

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u_dev, data = out_english)

KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = out_english)
plot_surv(KM_u_dev, data = out_english)
```

#### Looking at only device terms within freq_terms_a

```{r, echo = FALSE}
answered_devices <- freq_terms_a %>%
                      filter(word %in% c("screen", "iphone", "phone", "battery", "button", "display", "macbook", "lcd", "board", "keyboard", "laptop", "home", "pro", "drive"))

out_english$contain_dev_a <- str_detect(as.character(out_english$title), pattern = or1(answered_devices$word))
prop_contain_a_dev <- sum(out_english$contain_dev_a)/nrow(out_english)
```

* `r round(prop_contain_a_dev*100, 2)`% of titles contain at least 1 answered device term

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_dev_a, data = out_english)

KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = out_english)
plot_surv(KM_dev_a, data = out_english)
```

>>>>

---
title: "Functions Created"
author: "Lisa Oshita"
date: "July 21, 2017"
output: html_document
---

@@

```{r}
setup <- function() {
  dir <- file.path(getwd(),"data")
  out <- read.csv(file.path(dir, "answers_data.csv"))

@@

  out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
  empty <- which(is.na(out_english$time_until_answer))
  for (i in empty) {
    out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}
}

```

```{r}

plot_surv <- function(survfit, data) {

  library(ggfortify)
  library(directlabels)

@@
